\Large \bf Cyclone: Warp Speed Replication for Key Value Stores

### 2017-04-19 paper/paper.tex
Updates to paper.

\documentclass[10pt, preprint, nonatbib]{sigplanconf}
\usepackage{times,epsfig,endnotes,graphicx, verbatim}
\usepackage{datetime, url, hyperref, pdfpages}

@@

\begin{figure}
\centering
\includegraphics[scale=0.3]{figures2/nvm_log.pdf}
\hspace{-0.2in}
\caption{NVM Log Structure}
\label{fig:nvm_log}
\end{figure}

@@

The sequence of operations when a packet is received from the client however
needs careful design for efficient software packet switching. To illustrate how
this is achieved, Figure~\ref{fig:packet_layout} shows how Cyclone manipulates
packet layouts across the two steps of prepending a RAFT header and transmitting
to follower replicas. DPDK describes packets using an ``mbuf'' data
structure. Roughly speaking, an ``mbuf'' consists of a flat array of bytes
actually containing the byte and a fixed size piece of external metadata that
describes various aspects of the packet, most crucially a pointer to the start
and end of the packet in the byte array. DPDK's userspace drivers receive
packets from the NIC such that they are offset in the byte array by a
configurable amount referred to as ``headroom''. We prepend RAFT related
information in the headroom and shift the start pointer appropriately - these
operations are standard enough for software packet switches that DPDK provides
convenient library calls to do it. For the final step, we need to prepare the
packet for transmission to the various follower replicas. To do this we prepare
a different packet containing an ethernet header for the targeted replica and
``chain'' the data packet to each of these headers. Each header is then
separately handed off to the driver for transmission via the NIC.

@@

\begin{figure}
  \caption{Cyclone Network Packet Layout}
  \label{fig:packet_layout}
\end{figure}

TBD: talk about how we do not need a reliable network layer like TCP/IP.
\subsubsection{Batching}

>>>>

\documentclass[10pt, preprint, nonatbib]{sigplanconf}
\usepackage{times,epsfig,endnotes,graphicx, verbatim}
\usepackage{datetime, url, pdfpages}

@@

\begin{figure}
\centering
\includegraphics[scale=0.3]{figures2/nvm_log.pdf}
\caption{NVM Log Structure}
\label{fig:nvm_log}
\end{figure}

@@

The sequence of operations when a packet is received from the client however
needs careful design for efficient software packet switching. To illustrate how
this is achieved, Figure~\ref{fig:packet_layout} shows how Cyclone manipulates
packet layouts across the two steps of prepending a RAFT header and transmitting
to follower replicas. DPDK describes packets using an ``mbuf'' data
structure. Roughly speaking, an ``mbuf'' consists of a flat array of bytes
actually containing the byte and a fixed size piece of external metadata that
describes various aspects of the packet, most crucially a pointer to the start
and end of the packet in the byte array. DPDK's userspace drivers receive
packets from the NIC such that they are offset in the byte array by a
configurable amount referred to as ``headroom''. We prepend RAFT related
information specific to each log entry in the headroom and shift the start
pointer appropriately - these operations are standard enough for software packet
switches that DPDK provides convenient library calls to do it. For the final
step, we need to prepare the packet for transmission to the various follower
replicas. To do this we prepare a different packet containing an ethernet header
for the targeted replica and ``chain'' the data packet to each of these
headers. Each header is then separately handed off to the driver for
transmission via the NIC, carrying the data packet with it by association.

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.3]{figures2/network_packet.pdf}
  \caption{Cyclone Network Packet Layout}
  \label{fig:packet_layout}
\end{figure}

We note that by discrding stream oriented protocols the network layer is not
longer reliable or ordered. This is not a problem for RAFT that is designed to
tolerate network failures resulting in drops or reordering of network
packets. However this rules out consensus protocols such as Zookeeper Atomic
Broadcast (ZAB~\cite{zab}) that depend on a reliable stream-oriented network
layer to function correctly.

Finally, we turn our attention to the persistence step in
Figure~\ref{fig:control_plane}. RAFT requires that the log entry be persisted
before it is multicast out to follower replicas. Since the NVM is directly
attached we do this by executing a cacheline flush ({\tt clflush}) instruction
for every cacheline in the packet and the pointer in the pointer buffer to
persist these via the memory bus. This is the one exception to our otherwise
clean separation between the control and data plane - necessitated by the fact
that at the moment NICs do not support persistent memory. This is not too
onerous a burden because we can use the newly introduced {\tt
  clflush-opt}~\cite{clflush_opt} instruction specifically intended to
efficiently flush to persistent memory without the overhead of the serialization
normally introduced by {\tt clflush}. This allows one to hit full memory
bandwidth on present generation platforms, a quantity in excess of 200 Gb/s per
core, well above the near term speeds of network interface cards.

\subsubsection{Batching}
